Classifying Patents Based on their Semantic Content\thanks{Addresses: Bergeaud: Banque de France (antonin.bergeaud@banque-france.fr), Potiron: Keio University, Raimbault: ISC-PIF }

### 2018-11-10 Docs/Papers/Technical/overleafv2/main_v1.tex
slides_seminar

\documentclass[10pt,A4]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

@@

%\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{
\includegraphics[width=2.0in]{PLOS-submission-eps-converted-to.pdf}
}
\rhead{Classifying Patents Based on their Semantic Content\vspace{2mm}}
\rfoot{\thepage}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf Bergeaud, Potiron and Raimbault, 2017}
%\lfoot{}

@@

\usepackage[normalem]{ulem} % use normalem to protect \emph
\newcommand\hl{\bgroup\markoverwith
  {\textcolor{yellow}{\rule[-.5ex]{2pt}{2.5ex}}}\ULon}

@@

% writing utilities
%%%%%
% variable to include comments or not in the compilation ; set to 1 to include
%\def \draft {1}
\def \draft {0}

\def \trackdiff {1}
%\def \trackdiff {0}

% comments and responses
\usepackage{xparse}
\usepackage{ifthen}
\DeclareDocumentCommand{\comment}{m o o o o}
{\ifthenelse{\draft=1}{
    \textcolor{red}{\textbf{C : }#1}
    \IfValueT{#2}{\textcolor{blue}{\textbf{A1 : }#2}}
    \IfValueT{#3}{\textcolor{ForestGreen}{\textbf{A2 : }#3}}
    \IfValueT{#4}{\textcolor{red!50!blue}{\textbf{A3 : }#4}}
    \IfValueT{#5}{\textcolor{Aquamarine}{\textbf{A4 : }#5}}
 }{}
}

% todo
\newcommand{\todo}[1]{
\ifthenelse{\draft=1}{\textcolor{red!50!blue}{\textbf{TODO : \textit{#1}}}}{}
}

% track changes
\newcommand{\change}[1]{
\ifthenelse{\trackdiff=1}{\hl{#1}}{#1}
}

@@

\begin{flushleft}
{\Large
\textbf\newline{
Classifying Patents Based on their Semantic Content
}
}
\newline
\\
Antonin Bergeaud\textsuperscript{1,\Yinyang},
Yoann Potiron\textsuperscript{2,\Yinyang},
Juste Raimbault\textsuperscript{3,4,\Yinyang,*}
\\
\bigskip
\bf{1} Paris School of Economics - EHESS and Bank of France, Paris, France
\\
\bf{2} Faculty of Business and Commerce, Keio University, Tokyo, Japan
\\
\bf{3} UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Universit{\'e} Paris VII, Paris, France
\\
\bf{4} UMR-T 9403 IFSTTAR LVMT, Ecole Nationale des Ponts et Chauss{\'e}es, Champs-sur-Marne, France
\\
\bigskip

@@

\bigskip
%\newpage

@@

%%%%%%%%%%%%%%%%%%
\subsection{Data collection and basic description}
Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ format at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis. Indeed, the semantic analysis counts more than 4 million patents, with corresponding abstracts with an average length of 120.8 words (and a standard deviation of $62.4$), a size that is already challenging in terms of computational burden and data size. In addition, abstracts are aimed at synthesizing purpose and content of patents and must therefore be a relevant object of study (see~\cite{Adams2010text}). The USPTO defines a guidance stating that an abstract should be ``a summary of the disclosure as contained in the description, the claims, and any drawings; the summary shall indicate the technical field to which the invention pertains and shall be drafted in a way which allows the clear understanding of the technical problem, the gist of the solution of that problem through the invention, and the principal use or uses of the invention'' (PCT Rule 8).

We construct from raw data a unified database. Data is collected from USPTO patent redbook bulk downloads, that provides as raw data (specific \texttt{dat} or \texttt{xml} formats) full patent information, starting from 1976. Detailed procedure of data collection, parsing and consolidation are available in~\nameref{sectionSI}. The latest dump of the database in \texttt{Mongodb} format is available \change{at \url{http://dx.doi.org/10.7910/DVN/BW3ACK}.} Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.

@@

Finally, a semantic classification where patents are gathered based on the fact that they share similar significant keywords has the advantage of including a network feature that cannot be found in the USPC case, namely that each patent is associated with a vector of probability to belong to each of the semantic classes (more details on this feature can be found in Section \ref{characteristics}). Using co-occurrence of keywords, it is then possible to construct a network of patents and to study the influence of some key topological features. \change{As reviewed previously, the use of co-occurrences is the usual way to construct a semantic network. Other hybrid technique such as bipartite semantic/authors networks, do not have the nice feature of relying solely on endogenous semantic information contained in data.}

@@

Text processing operations are implemented in \texttt{python} in order to use built-in functions \texttt{nltk} library~\cite{nltk} for most of above operations. This library supports most of state-of-the-art natural language processing operations.\footnote{Source code is openly available on the repository of the project: \url{https://github.com/JusteRaimbault/PatentsMining} 
}

@@

Following the heuristic in~\cite{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem. The choice of the total number of keywords to be extracted, \change{which we shall denote $K_w$}, is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords. We choose to set this parameter to $K_w = 100,000$. We first consider the filtration of $k\cdot K_w$ (with $k=4$) to keep a large set of potential keywords but still have a reasonable number of co-occurrences to be computed. \change{This step has only very marginal effects on the nature of the final keywords but is necessary for computational purposes.} The filtration is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words. A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$, \change{where the formal definition can be found in (\ref{termhood})}. It is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus. Intuitively, uniformly distributed terms will be identified as plain language and they are thus not relevant for the classification. More precisely, we compute the co-occurrence matrix $(M_{ij})$, where $M_{ij}$ is defined as the number of patents where stems $i$ and $j$ appear together. The \emph{termhood} score $t_i$ is defined as

\begin{eqnarray}
\label{termhood}
t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
\end{eqnarray}

@@

where $k_j(s)$ is the number of occurrences of the $s$th keyword in each of the $j$th technological class taken from one of the $N^{(tec)}$ USPC classes. The higher $c_{tech}$, the more specific to a technological class the node is. For example, the terms \texttt{semiconductor} is widely used in electronics and does not contain any significant information in this field. We use a threshold parameter, \change{defined as $\theta_c$, and keep nodes with $c_{tech}(s) > \theta_c$. Likewise, edges with low weights correspond to rare co-occurrences and are considered to be noise. To account for this we define the threshold parameter for edges $\theta_w$, and we filter edges with a weight below $\theta_w$}, following the rationale that two keywords are not linked ``by chance'' if they appear simultaneously a minimal number of time. To control for size effect, we normalize by taking $\theta_w = \theta_w^{(0)}\cdot N_P$ where $N_P$ is the number of patents in the corpus ($N_P = \left|\mathcal{P} \right|$). \change{$\theta_w^{(0)}$ is thus a varying parameter interpreted as a noise threshold \emph{per patent}.} Communities are then extracted using a standard modularity maximization procedure as described in~\cite{clauset2004finding} to which we add the two constraints captured by $\theta_w$ and $\theta_c$, namely that edges must have a weight greater than $\theta_w$ and nodes a concentration greater than $\theta_c$. At this stage, both parameters $\theta_c$ and $\theta_w^{(0)}$ are unconstrained and their choice is not straightforward. Indeed, many optimization objectives are possible, such as the modularity, network size or number of communities. We find that modularity is maximized at a roughly stable value of $\theta_w$ across different $\theta_c$ for each year, corresponding to a stable $\theta_w^{(0)}$ across years, which leads us to choose $\theta_w^{(0)} = 4.1\cdot 10^{-5}$. Then for the choice of $\theta_c$, different candidates points lie on a Pareto front for the bi-objective optimization on number of communities and network size. \change{There is a priori no reason to choose any specific point among the different optimums. Consequently, we have tried the analysis with all the candidate values for $\theta_c$ and found that the results are the most reasonable when taking $\theta_c = 0.06$ (see Fig.~{\ref{fig:networksensitivity}}).}

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
%\includegraphics[width=\textwidth]{figures/Fig1}
\caption{\textbf{Sensitivity analysis of network community structure to filtering parameters.} We consider a specific window 2000-2004 and the obtained plots are typical. \textit{(Left panel)} We plot the number of communities as a function of the edge threshold parameter $\theta_w$ for different values of the node threshold parameter $\theta_c$. The maximum is roughly stable across $\theta_c$ (dashed red line). \textit{(Right panel)} To choose $\theta_c$, we do a Pareto optimization on communities and network size: the compromise point (red overline) on the Pareto front (purple overline: possible choices after having fixed $\theta_w^{(0)}$; blue level gives modularity) corresponds to $\theta_c = 0.06$.}
\label{fig:networksensitivity}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
%\includegraphics[width=\textwidth]{figures/Fig2}
\caption{\textbf{An example of semantic network visualization.} We show the network obtained for the window 2000-2004, with parameters $\theta_c = 0.06$ and $\theta_w = \theta_w^{(0)}\cdot N_P = 4.5e^{-5} \cdot 9.1e^{5}$. The corresponding file in a vector format (\texttt{.svg}), that can be zoomed and explored, is available as Supplementary Material.}
\label{fig:rawnetwork}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
%\includegraphics[width=\textwidth]{figures/Fig3}
\caption{\textbf{This figure plots the average number of keywords by semantic class for each time window $\left[t-4; t\right]$} from $t=1980$ to $t=2007$.}
\label{fig:mean_K}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\hspace*{-2.5cm}
%\includegraphics[width=\textwidth]{figures/Fig4}
\caption{\textbf{Sizes of classes.} Yearly from $t = 1980$ to $t =2007$, we plot the size of semantic classes (left-side) and technological classes (right-side) for the corresponding time window $[t-4, t]$, 
from the biggest to the smallest. The formal definition of size can be found in Section \ref{characteristics}. Each color corresponds to one specific year. Yearly semantic classes and technological classes present a similar hierarchical structure which confirms the comparability of the two classifications. This feature is crucial for the statistical analysis in Section \ref{statisticalmodel}. Over time, curves are translated and levels of hierarchy stays roughly constant.}
\label{fig:class-sizes}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

@@

Our use of network analysis can also be extended using newly developed techniques of hyper-network analysis. Indeed, patents and keywords can for example be nodes of a bipartite network, or patents be links of an hyper-network, in the sense of multiple layers with different classification links and citation links. \change{The combination of citation network modeling by Stochastic Block Modeling with topic modeling was studied for scientific papers by }\cite{zhu2013scalable}\change{, outperforming previous link prediction algorithms.} \cite{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network that could be applied as a refinement of the overlap, modularity and statistical modeling studied in this paper. Furthermore, is has recently been shown that measures of multilayer network projections induce a significant loss of information compared to the generalized corresponding measure~\cite{de2015ranking}, which confirms the relevance of such development that we left for further research.

\change{An other potential research development would be to further exploit the temporal structure of our dataset. Indeed, large progress have recently been made in complex network analysis of time-series data (see}~\cite{gao2017complex}\change{ for a review). For example, }\cite{gao2015multiscale}\change{develops a method to construct multiscale network from time series, which could in our case be a solution to identify structures in patents trajectories at different levels, and be an alternative to the single scale modularity analysis we use.}

@@

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
%\includegraphics[width=\textwidth]{figures/Fig5}
\caption{
\textbf{Patent level diversities.} Distributions of diversities (Left column) and corresponding mean time-series (Right column) for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$). The first row includes all classified patents, whereas the second row includes only patents with more than one class (i.e. patents with diversity greater than 0).
}
\label{fig:patent-level-orig}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
%\includegraphics[width=\textwidth]{figures/Fig6}
\caption{\textbf{Patent level originality} (left hand side) and \textbf{generality} (right hand side)  for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$) as defined in subsection \ref{subsec:orig-gene}. }
\label{fig:orig-gene}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\centering
%\includegraphics[width=\textwidth]{figures/Fig7}
\caption{
\textbf{Intra-Classification overlaps.}
(Left column) Distribution of overlaps $O_{ij}$ for all $i\neq j$ (zero values are removed because of the log-scale). Right column) Corresponding mean time-series. (First row) Normalized overlaps. (Second row) Relative overlaps.}
\label{fig:intra-classif-overlap}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
%\includegraphics[width=\textwidth]{figures/Fig8}
\caption{\textbf{Distribution of relative overlaps between classifications.} (Left) Distribution of overlaps at all time steps; (Right) Corresponding mean time-series. The decreasing trend starting around 1996 confirms a qualitative regime shift in that period.}
\label{fig:inter-classif-overlap}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\centering
%\includegraphics[width=\textwidth]{figures/Fig9}
\caption{\textbf{Temporal evolution of semantic and technological modularities of the citation network.} (Left) Simple directed modularity, computed with patent main classes (main technological class and semantic class with larger probability). (Right) Multi-class modularity, computed following~\cite{nicosia2009extending} }
\label{fig:modularities}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

@@

The main contribution of this study was twofold. First we have defined how we built a network of patents based on a classification that uses semantic information from abstracts. We have shown that this classification share some similarities with the traditional technological classification, but also have distinct features. Second, we provide researchers with materials resulting from our analysis, which includes: (i) a database linking each patent with its set of semantic classes and the associated probabilities; (ii) a list of these semantic classes with a description based on the most relevant keywords; (iii) a list of patent with their topological properties in the semantic network (centrality, frequency, degree, etc.). The availability of \change{this} data suggests new avenues for further research. \change{Linking our dataset with existing open ones can lead to various powerful developments. For example, using it together with the disambiguated inventor database provided by}~\cite{li2014disambiguation}\change{ could be a way to study semantic profiles of inventors, or of cities as inventor addresses are provided. The investigation of spatial diffusion of innovation between cities, which is a key component of Pumain's Evolutive Urban Theory}~\cite{pumain2010theorie}\change{, would be made possible.}

@@

\bibitem{martin2015}
Dechezlepr{\~A}ªtre A, Martin R, Mohnen M.
\newblock {Knowledge Spillovers from Clean and Dirty Technologies}.
\newblock Centre for Economic Performance, LSE; 2014. dp1300.
\newblock Available from:
  \url{https://ideas.repec.org/p/cep/cepdps/dp1300.html}.

@@

\bibitem{nltk}
NLTK. Natural Language Toolkit, Stanford Univeristy; 2015.

@@

\bibitem{zhu2013scalable}
Zhu Y, Yan X, Getoor L, Moore C.
\newblock Scalable text and link analysis with mixed-topic link models.
\newblock In: Proceedings of the 19th ACM SIGKDD international conference on
  Knowledge discovery and data mining. ACM; 2013. p. 473--481.

@@

\bibitem{gao2017complex}
Gao ZK, Small M, Kurths J.
\newblock Complex network analysis of time series.
\newblock EPL (Europhysics Letters). 2017;116(5):50001.

\bibitem{gao2015multiscale}
Gao ZK, Yang YX, Fang PC, Zou Y, Xia CY, Du M.
\newblock Multiscale complex network for analyzing experimental multivariate
  time series.
\newblock EPL (Europhysics Letters). 2015;109(3):30005.

@@

\bibitem{li2014disambiguation}
Li GC, Lai R, D’Amour A, Doolin DM, Sun Y, Torvik VI, et~al.
\newblock Disambiguation and co-authorship networks of the US patent inventor
  database (1975--2010).
\newblock Research Policy. 2014;43(6):941--955.

\bibitem{pumain2010theorie}
Pumain D.
\newblock Une th{\'e}orie g{\'e}ographique des villes.
\newblock Bulletin de la Soci{\'e}t{\'e} g{\'e}ographie de Li{\`e}ge.
  2010;(55):5--15.

@@

@@

>>>>

\documentclass[10pt,A4,draft]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

@@

%\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{
%\includegraphics[width=2.0in]{PLOS-submission-eps-converted-to.pdf}
}
\rfoot{\thepage}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
%\lfoot{\sf Bergeaud, Potiron and Raimbault, 2016 }
\lfoot{}

@@

@@

% writing utilities

% comments and responses
\usepackage{xparse}
\DeclareDocumentCommand{\comment}{m o o o o}
{%
    \textcolor{red}{#1}
    \IfValueT{#2}{\textcolor{blue}{#2}}
    \IfValueT{#3}{\textcolor{ForestGreen}{#3}}
    \IfValueT{#4}{\textcolor{red!50!blue}{#4}}
    \IfValueT{#5}{\textcolor{Aquamarine}{#5}}
}

% todo
\newcommand{\todo}[1]{\textcolor{red!50!blue}{\textbf{\textit{#1}}}}

@@

\begin{flushleft}
{\Large
\textbf\newline{
%An Hypernetwork Approach to Measure Technological Innovation
%Unveiling Endogenous Patterns of Technological Innovation
%Extracting Endogenous Information from Patent Semantic Data
%Patents Are Words: Extracting the Endogenous Information of Technological Innovation
%Classifying patents based on patent semantic content
%The Knowledge of Meaning Unveils the Meaning of Knowledge: Classifying Patents Based on their Semantic Content
Classifying Patents Based on their Semantic Content
% find a good title expressing both the multi-layer character and the novelty looking at semantic data
}
}
\newline
\\
Antonin Bergeaud\textsuperscript{1,\Yinyang},
Yoann Potiron\textsuperscript{2,\Yinyang},
Juste Raimbault\textsuperscript{3,4,\Yinyang,*}
\\
\bigskip
\bf{1} Department of Economics, London School of Economics, London, UK
\\
\bf{2} Faculty of Business and Commerce, Keio University, Tokyo, Japan
\\
\bf{3} UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Universit{\'e} Paris VII, Paris, France
\\
\bf{4} UMR-T 9403 IFSTTAR LVMT, Ecole Nationale des Ponts et Chauss{\'e}es, Champs-sur-Marne, France
\\
\bigskip

@@

\newpage

@@

%%%%%%%%%%%%%%%%%%
\subsection{Data collection and basic description}
Each patent contains an abstract and a core text which describe the invention.\footnote{To see what a patent looks like in practice, one can refer to the USPTO patent full-text database \url{http://patft.uspto.gov/netahtml/PTO/index.html} or to Google patent which publishes USPTO patents in $pdf$ form at \url{https://patents.google.com}.} Although including the full core texts would be natural and probably very useful in a systematic text-mining approach as done in~\cite{tseng2007text}, they are too long to be included and thus we consider only the abstracts for the analysis. Indeed, the semantic analysis counts more than 4 million patents, with corresponding abstracts with an average length of 120.8 words (and a standard deviation of $62.4$), a size that is already challenging in terms of computational burden and data size. In addition, abstracts are aimed at synthesizing purpose and content of patents and must therefore be a relevant object of study (see~\cite{Adams2010text}). The USPTO defines a guidance stating that an abstract should be ``a summary of the disclosure as contained in the description, the claims, and any drawings; the summary shall indicate the technical field to which the invention pertains and shall be drafted in a way which allows the clear understanding of the technical problem, the gist of the solution of that problem through the invention, and the principal use or uses of the invention'' (PCT Rule 8).

We construct from raw data a unified database. Data is collected from USPTO patent redbook bulk downloads, that provides as raw data (specific \texttt{dat} or \texttt{xml} formats) full patent information, starting from 1976. Detailed procedure of data collection, parsing and consolidation are available in~\nameref{sectionSI}. The latest dump of the database in \texttt{Mongodb} format is available at \url{http://37.187.242.99/files/public/USPTOredbook.gz}.
%\url{http://dx.doi.org/10.7910/DVN/BW3ACK} % keep the dataverse hidden for now
Collection and homogenization of the database into a directly usable database with basic information and abstracts was an important task as USPTO raw data formats are involved and change frequently.

@@

Finally, a semantic classification where patents are gathered based on the fact that they share similar significant keywords has the advantage of including a network feature that cannot be found in the USPC case, namely that each patent is associated with a vector of probability to belong to each of the semantic classes (more details on this feature can be found in Section \ref{characteristics}). Using co-occurrence of keywords, it is then possible to construct a network of patents and to study the influence of some key topological features.

@@

Text processing operations are implemented in \texttt{python} in order to use built-in functions \texttt{nltk} library~\cite{nltk} for most of above operations. This library supports most of state-of-the-art natural language processing operations.\footnote{Source code is openly available on the repository of the project: \url{https://github.com/AnonymousAuthor1/PatentsMining} 
}

@@

Following the heuristic in~\cite{chavalarias2013phylomemetic}, we estimate relevance score in order to filter multi-stem. The choice of the total number of keywords to be extracted $K_w$ is important, too small a value would yield similar network structures but including less information whereas very large values tend to include too many irrelevant keywords. We choose to set this parameter to $K_w = 100,000$. We first consider the filtration of $k\cdot K_w$ (with $k=4$) to keep a large set of potential keywords but still have a reasonable number of co-occurrences to be computed. This is done on the \emph{unithood} $u_i$, defined for keyword $i$ as $u_i = f_i\cdot \log{(1 + l_i)}$ where $f_i$ is the multi-stem's number of apparitions over the whole corpus and $l_i$ its length in words. A second filtration of $K_w$ keywords is done on the \emph{termhood} $t_i$. The latter is computed as a chi-squared score on the distribution of the stem's co-occurrences and then compared to a uniform distribution within the whole corpus. Intuitively, uniformly distributed terms will be identified as plain language and they are thus not relevant for the classification. More precisely, we compute the co-occurrence matrix $(M_{ij})$, where $M_{ij}$ is defined as the number of patents where stems $i$ and $j$ appear together. The \emph{termhood} score $t_i$ is defined as

\[
t_i = \sum_{j\neq i}\frac{\left( M_{ij} - \sum_{k}M_{ik} \sum_{k} M_{jk}\right)^2}{\sum_{k}M_{ik} \sum_{k} M_{jk}}.
\]

@@

where $k_j(s)$ is the number of occurrences of the $s$th keyword in each of the $j$th technological class taken from one of the $N^{(tec)}$ USPC classes. The higher $c_{tech}$, the more specific to a technological class the node is. For example, the terms \texttt{semiconductor} is widely used in electronics and does not contain any significant information in this field. We use a threshold parameter and keep nodes with $c_{tech}(s) > \theta_c$. In a similar manner, edge with low weights correspond to rare co-occurrences and are considered as noise: we filter edges with weight lower than a threshold $\theta_w$, following the rationale that two keywords are not linked ``by chance'' if they appear simultaneously a minimal number of time. To control for size effect, we normalize by taking $\theta_w = \theta_w^{(0)}\cdot N_P$ where $N_P$ is the number of patents in the corpus ($N_P = \left|\mathcal{P} \right|$). Communities are then extracted using a standard modularity maximization procedure as described in~\cite{clauset2004finding} to which we add the two constraints captured by $\theta_w$ and $\theta_c$, namely that edges must have a weight greater than $\theta_w$ and nodes a concentration greater than $\theta_c$. At this stage, both parameters $\theta_c$ and $\theta_w^{(0)}$ are unconstrained and their choice is not straightforward. Indeed, many optimization objectives are possible, such as the modularity, network size or number of communities. We find that modularity is maximized at a roughly stable value of $\theta_w$ across different $\theta_c$ for each year, corresponding to a stable $\theta_w^{(0)}$ across years, which leads us to choose $\theta_w^{(0)} = 4.1\cdot 10^{-5}$. Then for the choice of $\theta_c$, different candidates points lie on a Pareto front for the bi-objective optimization on number of communities and network size, among which we take $\theta_c = 0.06$ (see Fig.~\ref{fig:networksensitivity}).

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
%\hspace{-2.5cm}
%\includegraphics[width=0.45\textwidth,height=0.25\textheight]{figures/comnum_thetaw_2004.png}
%\includegraphics[width=0.45\textwidth,height=0.25\textheight]{figures/comnum_vcount_pareto_2004.png}
%\includegraphics[width=\textwidth]{tiff/Fig1.tif}
\caption{\textbf{Sensitivity analysis of network community structure to filtering parameters.} We consider a specific window 2000-2004 and the obtained plots are typical. \textit{(Left panel)} We plot the number of communities as a function of $\theta_w$ for different $\theta_c$ values. The maximum is roughly stable across $\theta_c$ (dashed red line). \textit{(Right panel)} To choose $\theta_c$, we do a Pareto optimization on communities and network size: the compromise point (red overline) on the Pareto front (purple overline: possible choices after having fixed $\theta_w^{(0)}$; blue level gives modularity) corresponds to $\theta_c = 0.06$.}
\label{fig:networksensitivity}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
%\includegraphics[width=0.75\textwidth]{figures/graph-filtered_2000-2004_kwLimit100000_dispth0_06_ethunit4_5e-05_LOWRES}
%\includegraphics[width=\textwidth]{tiff/Fig2.tif}
\caption{\textbf{An example of semantic network visualization.} We show the network obtained for the window 2000-2004, with parameters $\theta_c = 0.06$ and $\theta_w = \theta_w^{(0)}\cdot N_P = 4.5e^{-5} \cdot 9.1e^{5}$. The corresponding file in a vector format (\texttt{.svg}), that can be zoomed and explored, is available as Supplementary Material.}
\label{fig:rawnetwork}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
%\includegraphics[width=0.9\textwidth]{figures/meancomsize}
%\includegraphics[width=\textwidth]{tiff/Fig3.tif}
\caption{\textbf{This figure plots the average number of keywords by semantic class for each time window $\left[t-4; t\right]$} from $t=1980$ to $t=2007$.}
\label{fig:mean_K}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\hspace*{-2.5cm}
%\includegraphics[width=1.2\textwidth]{figures/all_raw_counts.png}
%\includegraphics[width=\textwidth]{tiff/Fig4.tif}
\caption{\textbf{Sizes of classes.} Yearly from $t = 1980$ to $t =2007$, we plot the size of semantic classes (left-side) and technological classes (right-side) for the corresponding time window $[t-4, t]$, 
from the biggest to the smallest. The formal definition of size can be found in Section \ref{characteristics}. Each color corresponds to one specific year. Yearly semantic classes and technological classes present a similar hierarchical structure which confirms the comparability of the two classifications. This feature is crucial for the statistical analysis in Section \ref{statisticalmodel}. Over time, curves are translated and levels of hierarchy stays roughly constant.}
\label{fig:class-sizes}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

@@

Our use of network analysis can also be extended using newly developed techniques of hyper-network analysis. Indeed, patents and keywords can for example be nodes of a bipartite network, or patents be links of an hyper-network, in the sense of multiple layers with different classification links and citation links. \cite{iacovacci2015mesoscopic} provide a method to compare macroscopic structures of the different layers in a multilayer network that could be applied as a refinement of the overlap, modularity and statistical modeling studied in this paper. Furthermore, is has recently been shown that measures of multilayer network projections   induce a significant loss of information compared to the generalized corresponding measure~\cite{de2015ranking}, which confirms the relevance of such development that we left for further research.

@@

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
%First row : semantic with relevant keywords only - all patents 
%\includegraphics[width=0.49\textwidth]{figures/patentlevelorigs_all_semcounts}
%\includegraphics[width=0.49\textwidth]{figures/patentlevelorigs_all_ts_semcounts}\\
%Second row : patents with diversity $> 0$ (more than one class)}
%\includegraphics[width=0.49\textwidth]{figures/patentlevelorigs_positive_semcounts}
%\includegraphics[width=0.49\textwidth]{figures/patentlevelorigs_positive_ts_semcounts}
%\includegraphics[width=\textwidth]{tiff/Fig5.tif}
\caption{
\textbf{Patent level diversities.} Distributions of diversities (Left column) and corresponding mean time-series (Right column) for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$). The first row includes all classified patents, whereas the second row includes only patents with more than one class (i.e. patents with diversity greater than 0).
}
\label{fig:patent-level-orig}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
%\includegraphics[width=0.49\textwidth]{figures/originality.png}
%\includegraphics[width=0.49\textwidth]{figures/generality.png}\\
%\includegraphics[width=\textwidth]{tiff/Fig6.tif}
\caption{\textbf{Patent level originality} (left hand side) and \textbf{generality} (right hand side)  for $t=1980$ to $t=2007$ (with the corresponding time window $[t-4,t]$) as defined in subsection \ref{subsec:orig-gene}. }
\label{fig:orig-gene}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\centering
%\includegraphics[width=0.49\textwidth]{figures/norm-patents_all_density_semcounts.png}
%\includegraphics[width=0.49\textwidth]{figures/norm-patents_all_ts_semcounts.png} \\
%\includegraphics[width=0.49\textwidth]{figures/relative_all_density_semcounts.png}
%\includegraphics[width=0.49\textwidth]{figures/relative_all_ts_semcounts.png} 
%\includegraphics[width=\textwidth]{tiff/Fig7.tif}
\caption{
\textbf{Intra-classification overlaps.}
\textit{(Left column)} Distribution of overlaps $O_{ij}$ for all $i\neq j$ (zero values are removed because of the log-scale). \textit{(Right column)} Corresponding mean time-series. \textit{(First row)} Normalized overlaps. \textit{(Second row)} Relative overlaps.}
\label{fig:intra-classif-overlap}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
%\includegraphics[width=0.49\textwidth]{figures/relative_interclassif_all_density_semcounts.png}
%\includegraphics[width=0.49\textwidth]{figures/relative_interclassif_all_ts_semcounts.png}
%\includegraphics[width=\textwidth]{tiff/Fig8.tif}
\caption{\textbf{Distribution of relative overlaps between classifications.} (Left) Distribution of overlaps at all time steps; (Right) Corresponding mean time-series. The decreasing trend starting around 1996 confirms a qualitative regime shift in that period.}
\label{fig:inter-classif-overlap}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!ht]
\centering
%\includegraphics[width=0.49\textwidth]{figures/simplemodularity}
%\includegraphics[width=0.49\textwidth]{figures/overlappingmodularity}
%\includegraphics[width=\textwidth]{tiff/Fig9.tif}
\caption{\textbf{Temporal evolution of semantic and technological modularities of the citation network.} (Left) Simple directed modularity, computed with patent main classes (main technological class and semantic class with larger probability). (Right) Multi-class modularity, computed following~\cite{nicosia2009extending} }
\label{fig:modularities}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%

@@

The main contribution of this study was twofold. First we have defined how we built a network of patents based on a classification that uses semantic information from abstracts. We have shown that this classification share some similarities with the traditional technological classification, but also have distinct features. Second, we provide researchers with materials resulting from our analysis, which includes: (i) a database linking each patent with its set of semantic classes and the associated probabilities; (ii) a list of these semantic classes with a description based on the most relevant keywords; (iii) a list of patent with their topological properties in the semantic network (centrality, frequency, degree etc...). The availability of these data suggests new avenues for further research.

@@

\bibitem{martin2015}
Dechezlepretre A, Martin R, Mohnen M.
\newblock {Knowledge Spillovers from Clean and Dirty Technologies}.
\newblock Centre for Economic Performance, LSE; 2014. dp1300.
\newblock Available from:
  \url{https://ideas.repec.org/p/cep/cepdps/dp1300.html}.

@@

\bibitem{nltk}
NLTK. Natural Language Toolkit, Stanford University; 2015.

@@

@@

@@

@@

\bibitem{regibeau2010}
R{\'e}gibeau P, Rockett K.
\newblock Innovation cycles and learning at the patent office: does the early
  patent get the delay?
\newblock Journal of Industrial Economics. 2010;58(2):222--246.
\newblock Available from:
  \url{http://EconPapers.repec.org/RePEc:bla:jindec:v:58:y:2010:i:2:p:222-246}.

@@

\subsection{Semantic Communities Dynamics \label{subsec:semantic-flows}}
